Simulating dynein's powerstroke using Brownian dynamics

### 2017-05-13 thesis/latex/thesis.tex
Thesis: minor cleanup.

\section{Motivation}
Motor proteins are cellular structures which use chemical energy to do work and generate motion. Kinesin, myosin and dynein are the three main motor proteins in cells. Though these proteins have significantly different ancestors \ref{hook-family}, they all evolved into a single similar structure. In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way of solving a problem. How, then, do motor proteins work?\\

@@

Neurons have cell bodies at their centers and axons which grow outwards. Axons are long, narrow structures extending up to a meter in length in humans. Cell bodies contain nuclei and important organelles for synthesizing proteins, but growth of axon tips is vital for neuron function. This means bidirectional motor transport between axon tips and cell bodies is very important in neurons, since diffusion would not be quick enough. Retrograde transport is transport from the axon tip to the cell body. Cargo includes vesicles full of proteins ready to be broken down in the cell body and microtubule fragments to be returned from the axon tip \cite{neuroanatomy}. Because microtubule minus ends are found in the cell body, dynein's minus end-directed nature makes it the only protein capable of retrograde transport. An interesting question is, if proteins like dynein are synthesized in the cell body but needed at the axon tip to perform retrograde transport, how do dynein get to the tip? The answer is shown in \ref{retrograde-transport}: kinesin, a plus end-directed motor, takes dynein to the tip from the cell body.\\

@@

\subsection{Dynein structure}
As shown in the crystal structure in Figure \ref{fig:pdb-motm-dynein}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains. Each of these subunits has a unique purpose for the motor.\\

Dynein is a fusion of two identical proteins, referred to as monomers. A single monomer, depicted in \ref{fig:pdb-motm-dynein}, is composed of a microtubule-binding domain (MTBD), a stalk, a buttress, a motor domain, a linker and a tail. The MTBD is responsible for binding to the microtubule. The stalk links the motor domain to the MTBD and carries information about the state of the motor to the MTBD. The motor domain hydrolyses ATP and performs the main conformation changes involved in the step \cite{FRETstatepaper}. The linker connects the tail to the motor and also changes conformation during the step. The tail is a binding site which interacts with several binding partners, including the tail of a twin monomer.\\

@@

A major factor which could contribute to differences in stepping is each protein's size. Kinesin proteins are generally 100-200 kD in mass, whereas dynein is on the order of 1mD. As shown in Figure \ref{fig:kinesin-vs-dynein}, the dynein motor domain is much bigger than the kinesin motor domain. Another key difference is the separation between ATP hydrolysis sites on either protein. Kinesin's ATP hydrolysis site is inside the globular microtubule-binding domain. In contrast, Dynein binds to the MT with its MTBD, colored yellow in Figure \ref{fig:kinesin-vs-dynein}, and hydrolyses ATP in its motor domain, which is colored cyan. This distance is close to 20nm in length - much longer than kinesin. This large separation might act like a loose ``leash,'' allowing the binding domain to diffuse freely around the microtubule. Kinesin has a much more rigid leash, as shown in the bottom pane of \ref{fig:kinesin-vs-dynein}. This more rigid leash may prevent diffusion from happening as much.\\

\begin{figure}[H]
  \centering
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein}
  \end{minipage}
  \begin{minipage}{0.65\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein_2}
  \end{minipage}
  \caption{Structural comparison of dynein and kinesin}{Left: Comparison of crystal structures of the motor domains of dynein and kinesin bound to a microtubule. Image from \cite{kinesin-vs-dynein}. Right: Full motor complexes of dynein and kinesin. The blue regions of either protein are the motor domains, which are pictured in the above crystal structures. Image from \cite{kinesin-vs-dynein-2}.}
  \label{fig:kinesin-vs-dynein}
\end{figure}

@@

Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the trail \cite{FRETstatepaper} \cite{burgess-paper}. Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/burgess-dynein-angles}\\
  \hspace{1cm}
  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/linker-swing}
  \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states. Top left: dynein frozen in ADP-Pi state. Top middle: dynein without nucleotide. Top right: two states superimposed on one another. Figures borrowed from \cite{burgess-paper}. Bottom: X-ray diffraction-inspired image of a motor in two nucleotide states. Bottom left: motor in ADP-Pi state. Bottom right: Motor in ADP state. The linker undergoes an approximately 40 degree swing between these two states. Figure borrowed from \cite{bhabha-paper}.}
  \label{fig:cryo-em-angles}
\end{figure}

Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper} (make a Chimaera figure where the pre/poststroke motors are docked showing this). Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.\\

@@

Cianfrocco \textit{et. al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig. \ref{mech-cycle}. The model claims the primary events in the dynein step are as follows. First, starting with both binding domains attached to the MT, ATP binds to the motor domain, which causes it to change conformation. ATP hydrolysis to ADP-Pi causes further conformation changes. These changes cause the binding domain to release the microtubule, meaning only one binding domain is MT-bound. The free binding domain then undergoes another conformation change known as the ``priming stroke,'' which changes the orientation of the binding domain with respect to the MT. Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle. The exact order of these events is not precisely known.\\

@@

\section{Testing the Cianfrocco model}
One of the main goals of studying dynein is establishing how the motor walks. This can be a difficult task, since direct observation of the protein walking is not currently experimentally possible. Given the experimental challenges, a computational approach seems promising. This approach involves creating a hypothesis on how the motor walks, creating a model which behaves according to this hypothesis, simulating that model, and comparing the simulation's behavior to experimental data. This process can be an efficient way to support hypotheses and guide future research.\\

@@

\section{Model overview}
The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model \ref{sec:cianfrocco-model} would behave in a cell. In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation. Creating such a model is a balance between accuracy and computational efficiency. The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time. Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be prohibitively expensive to simulate a dynein step. Thus, many approximations are made about dynein to simplify the simulation.\\

@@

\subsection{Summary}
The model is composed of two separate systems of five point particles, with each point representing a domain of dynein: two binding domains, two motor domains and one tail domain. Physical representations of these two systems are shown in Figure \ref{fig:theory-intro}. The points are connected together by rigid rods, and the sytems are defined by the angles the rods make at each point. These angles are free to swivel. Each point thus acts somewhat like a ``hinge'' which can open or close. These two systems represent different modes dynein can be in. The Cianfrocco model is simplified to two states: onebound, when one MTBD (Microtubule Binding Domain) is diffusively searching for a binding site, and bothbound, where both MTBDs are MT-bound. The model can be in one of these two states at any time, and can transition between them if the right conditions are met. For example, if the model is in the onebound state but drifts such that both of its MTBDs are near the microtubule, the model can ``bind'' the MT and transition to the bothbound state.\\

@@

As shown in Figure \ref{fig:pdb-motm-dynein}, dynein's motor and tail domains are fairly spherical. Though the stalk and tail connecting these domains is definitely not massless, it is small enough that approximating it as massless should be reasonable. Making the radii of the spherical domains slightly larger should account for any drag caused by the rigid rods.

@@

\subsection{Rods connecting domains are rigid}
The model assumes connected domains are rigidly attached to one another by rods. This assumption makes the math easier. One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \ref{burgess-paper}. However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \ref{myosin-cc-elasticity}. Another dynein simulation done by Sarlah \textit{et. al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}.\\

@@

This energy represents the conformational energy of that particular domain. This energy can be used to calculate a return force which pushes the domain back to equilibrium. A depiction of this is shown in Figure \ref{fig:angular-spring}.\\

@@

\subsection{2D model}
The coordinate system for this model is two-dimensional. Thus interactions between the two motors and MTBDs are ignored. This assumption is made to simplify the model. Other dynein models, like the winch model \ref{sarlahmodel}, add in attractive and repulsive forces between the two motors which act in three dimensions. This model ignores such effects.\\

@@

Thus, if velocity equations can be found for the individual domains, then dynein's dynamic behavior can be solved for using numerical integration. The Brownian dynamics equation shown in Section \ref{sec:bd} provides velocity at time t from forces at time t. All that needs to be done is to come up with expressions for the forces on each domain, which is done in the next two sections.\\

@@

\subsection{Prestroke onebound model}
Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound. A spatial representation of onebound dynein is shown in Figure \ref{fig:derivation-onebound}.

@@

As shown in Section \ref{final-parameter-table}, the MT binding rate is much quicker than the unbinding rate. This means that, when just unbound, the rate of rebinding is very high. To prevent immediate rebinding, the model is given a ``rebinding immunity'' of a single timestep. During this immunity period, rebinding is not allowed.\\

@@

A series of conformational tests were done to test if the coordinate systems of either model worked. These are listed in Appendix \ref{sec:conformational-tests}.\\

@@

To test if the models obey the ET, the total potential energy of each model was logged over $10^7$ timesteps of simulation. The results are reported in Figure \ref{equipartition_agreement}, where the PE scale is in units of $\frac12 k_bT$. Energies are reported as a running average over the simulation from 0 to time $t$. As shown, both models have their average potential energy converge to the expected amount, where the onebound model has four degrees of freedom and the bothbound two.\\

@@

\section{Parameter fitting}
There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\theta_{m,eq}^{Pre}$, $\theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$. Each of these values influences the stepping behavior of the model, and so must be chosen wisely. Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}. Others are more difficult to find. These values, including $k_b$, $k_ub$ and the three spring constants, must be found via fitting the model to experiment.\\

@@

\section{Model achieves processivity}
When the simulation is run at the parameters shown in \ref{table:thesis-parameters}, the model exhibits stepping behavior, as shown in Figure \ref{fig:stepping-trajectory}.\\

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$ & dt\\\hline
    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$ & $10^{-10}s$\\ \hline
  \end{tabular}
  \caption{Parameters used in processive simulations.}{These parameters cause processive stepping in the dynein model, as shown in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
  \label{table:thesis-parameters}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
  \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation. The blue foot corresponds to the ``near'' dimer closer to the viewer, and the red to the far dimer. Top: x-projection of binding domains over time. The motor steps roughly 50nm in 10 $\mu s$. Middle: cartoon depictions of the model during simulation. In the cartoons the blue foot's position on the x-axis corresponds to the time axis on the top and bottom plots. That is, the first cartoon corresponds to dynein at roughly 1 $\mu s$. The first cartoon corresponds to a bothbound model, and the second cartoon corresponds to a onebound model. Bottom: y-projection of binding domains over time. Notice that only one binding domain is above 0nm at any time.}
  \label{fig:stepping-trajectory}
\end{figure}

Figures \ref{fig:stepping-trajectory}.b and \ref{fig:stepping-trajectory}.c demonstrate the model stepping five times, where a step constitutes lifting a binding domain off the microtubule for any amount of time. This behavior indicates that a springy hinge model with shifting equilibrium angles is capable of generating processive stepping behavior. Now that the model has demonstrated stepping behavior, it must be seen if it can generate steps at a size- and time-scale similar to that which real dynein takes in experiment.\\

Another important determination from Figure \ref{fig:stepping-trajectory}.c is the average position of the unbound foot is about 30\textit{nm} above the microtubule. This is a preliminary finding which may not represent how the model will behave once fit to stepping behavior, so drawing conclusive conclusions from it is impossible. However, it does initially suggest how dynein searches for the microtubule. Instead of hovering near the microtubule looking for a binding site, the motor pulls its foot away from the microtubule, diffusing until pushed downward far enough to bind. This behavior could explain why dynein's stepping pattern is so large: diffusing downward from 30\textit{nm} would allow significant x-diffusion along the microtubule. This could be contrasted with kinesin, which is smaller and could not move its foot so high off the microtubule.\\

@@

\section{Model step size is highly variant}
Figure \ref{fig:final-histograms} shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}. This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model. Note the model can generate 25nm steps, but has a high preference for <5nm steps. Also note that no backward steps are generated by the model. Simulation run at conditions in \ref{table:thesis-parameters}. Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
    \label{fig:final-histograms}
\end{figure}

Figure \ref{fig:final-histograms} shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$. This is a very important result, since it indicates that the model is capable of taking a varied step size. This behavior is characteristic of dynein, and hence very important to reproduce.\\

The preference for $<5nm$ steps is very un-dynein-like. One explanation is that steps may be defined differently between experimental and modeled dynein. In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram. This may not be how the experiment in \ref{fig:final-histograms} records steps. Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely. A solution would thus be to lower the microtubule binding rate and see if the stepping histogram would level out. This may help, but may not, since lowering the binding rate would affect all binding probabilities, not just immediate rebindings.\\

@@

Comparing the simulation results in \ref{fig:final-histograms} with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein. However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein. It is very possible that changing the binding rate, unbinding rate and spring constants will change the stepping behavior of the model dramatically. Lowering the binding rate may even out the histogram and prevent instant rebinding. It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm. Another issue is the lack of backwards steps, which may also be solved by altering the spring constants.\\

>>>>

\section{Motivation}
Motor proteins are cellular structures which use chemical energy to do work and generate motion. Kinesin, myosin and dynein are the three main motor proteins in cells. Though these proteins have significantly different ancestors \cite{hook-family}, they all evolved into a single similar structure. In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way of solving a problem. How, then, do motor proteins work?\\

@@

Neurons have cell bodies at their centers and axons which grow outwards. Axons are long, narrow structures extending up to a meter in length in humans. Cell bodies contain nuclei and important organelles for synthesizing proteins, but growth of axon tips is vital for neuron function. This means bidirectional motor transport between axon tips and cell bodies is very important in neurons, since diffusion would not be quick enough. Retrograde transport is transport from the axon tip to the cell body. Cargo includes vesicles full of proteins ready to be broken down in the cell body and microtubule fragments to be returned from the axon tip \cite{neuroanatomy}. Because microtubule minus ends are found in the cell body, dynein's minus end-directed nature makes it the only protein capable of retrograde transport. An interesting question is, if proteins like dynein are synthesized in the cell body but needed at the axon tip to perform retrograde transport, how do dynein get to the tip? The answer is shown in Figure (\ref{retrograde-transport}): kinesin, a plus end-directed motor, takes dynein to the tip from the cell body.\\

@@

\subsection{Dynein structure}
As shown in the crystal structure in Figure (\ref{fig:pdb-motm-dynein}), a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains. Each of these subunits has a unique purpose for the motor.\\

Dynein is a fusion of two identical proteins, referred to as monomers. A single monomer, depicted in (\ref{fig:pdb-motm-dynein}), is composed of a microtubule-binding domain (MTBD), a stalk, a buttress, a motor domain, a linker and a tail. The MTBD is responsible for binding to the microtubule. The stalk links the motor domain to the MTBD and carries information about the state of the motor to the MTBD. The motor domain hydrolyses ATP and performs the main conformation changes involved in the step \cite{FRETstatepaper}. The linker connects the tail to the motor and also changes conformation during the step. The tail is a binding site which interacts with several binding partners, including the tail of a twin monomer.\\

@@

A major factor which could contribute to differences in stepping is each protein's size. Kinesin proteins are generally 100-200 kD in mass, whereas dynein is on the order of 1mD. As shown in Figure (\ref{fig:kinesin-vs-dynein}), the dynein motor domain is much bigger than the kinesin motor domain. Another key difference is the separation between ATP hydrolysis sites on either protein. Kinesin's ATP hydrolysis site is inside the globular microtubule-binding domain. In contrast, Dynein binds to the MT with its MTBD, colored yellow in Figure (\ref{fig:kinesin-vs-dynein}), and hydrolyses ATP in its motor domain, which is colored cyan. This distance is close to 20nm in length - much longer than kinesin. This large separation might act like a loose ``leash,'' allowing the binding domain to diffuse freely around the microtubule. Kinesin has a much more rigid leash, as shown in the bottom pane of (\ref{fig:kinesin-vs-dynein}). This more rigid leash may prevent diffusion from happening as much.\\

\begin{figure}[H]
  \centering
  \begin{minipage}{0.3\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein}
  \end{minipage}
  \begin{minipage}{0.65\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein_2}
  \end{minipage}
  \caption{Structural comparison of dynein and kinesin}{Left: Comparison of crystal structures of the motor domains of dynein and kinesin bound to a microtubule. Image from \cite{kinesin-vs-dynein}. Right: Full motor complexes of dynein and kinesin inspired by cryo-EM microscopy. The blue regions on the right image of either protein are the motor domains, which are pictured in the left crystal structures. Not present in the left cyrstal structures are the tail and intermediate chains of either protein. Right image from \cite{kinesin-vs-dynein-2}.}
  \label{fig:kinesin-vs-dynein}
\end{figure}

@@

Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the tail \cite{FRETstatepaper} \cite{burgess-paper}. Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state. The shifting of the linker domain in the ADP state is known as the powerstroke, and is believed to be the principle cause for dynein's forward step.\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/burgess-dynein-angles}\\
  \hspace{1cm}
  \includegraphics[width=.95\textwidth,keepaspectratio]{../../figures/linker-swing}
  \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states. Top left: dynein frozen in ADP-Pi state. Top middle: dynein without nucleotide. Top right: two states superimposed on one another. Figures borrowed from \cite{burgess-paper}. Bottom: X-ray diffraction-inspired image of a motor in two nucleotide states. Bottom left: motor in ADP-Pi state. Bottom right: Motor in ADP state. The linker undergoes an approximately 40 degree swing between these two states known as the powerstroke. Figure borrowed from \cite{bhabha-paper}.}
  \label{fig:cryo-em-angles}
\end{figure}

Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}. Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.\\

@@

Cianfrocco \textit{et. al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig. (\ref{mech-cycle}). The model claims the primary events in the dynein step are as follows. First, starting with both binding domains attached to the MT, ATP binds to the motor domain, which causes it to change conformation. ATP hydrolysis to ADP-Pi causes further conformation changes. These changes cause the binding domain to release the microtubule, meaning only one binding domain is MT-bound. The free binding domain then undergoes another conformation change known as the ``priming stroke,'' which changes the orientation of the binding domain with respect to the MT. Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle. The exact order of these events is not precisely known.\\

@@

\section{Testing the Cianfrocco model}
One of the main goals of studying dynein is establishing how the motor walks. This can be a difficult task, since direct observation of the protein walking is not currently experimentally possible. Given the experimental challenges, a computational approach seems promising. This approach involves forming a hypothesis on how the motor walks, creating a model which behaves according to this hypothesis, simulating that model, and comparing the simulation's behavior to experimental data. This process can be an efficient way to support hypotheses and guide future research.\\

@@

\section{Model overview}
The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model (\ref{sec:cianfrocco-model}) would behave in a cell. In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation. Creating such a model is a balance between accuracy and computational efficiency. The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time. Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be prohibitively expensive to simulate a dynein step. Thus, many approximations are made about dynein to simplify the simulation.\\

@@

\subsection{Summary}
The model is composed of two separate systems of five point particles, with each point representing a domain of dynein: two binding domains, two motor domains and one tail domain. Physical representations of these two systems are shown in Figure (\ref{fig:theory-intro}). The points are connected together by rigid rods, and the sytems are defined by the angles the rods make at each point. These angles are free to swivel. Each point thus acts somewhat like a ``hinge'' which can open or close. These two systems represent different modes dynein can be in. The Cianfrocco model is simplified to two states: onebound, when one MTBD (Microtubule Binding Domain) is diffusively searching for a binding site, and bothbound, where both MTBDs are MT-bound. The model can be in one of these two states at any time, and can transition between them if the right conditions are met. For example, if the model is in the onebound state but drifts such that both of its MTBDs are near the microtubule, the model can ``bind'' the MT and transition to the bothbound state.\\

@@

As shown in Figure (\ref{fig:pdb-motm-dynein}), dynein's motor and tail domains are fairly spherical. Though the stalk and tail connecting these domains is definitely not massless, it is small enough that approximating it as massless should be reasonable. Making the radii of the spherical domains slightly larger should account for any drag caused by the rigid rods.\\

@@

\subsection{Rods connecting domains are rigid}
The model assumes connected domains are rigidly attached to one another by rods. This assumption makes the math easier. One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \cite{burgess-paper}. However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \cite{myosin-cc-elasticity}. Another dynein simulation done by Sarlah \textit{et. al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}.\\

@@

This energy represents the conformational energy of that particular domain. This energy can be used to calculate a return force which pushes the domain back to equilibrium. A depiction of this is shown in Figure (\ref{fig:angular-spring}).\\

@@

\subsection{2D model}
The coordinate system for this model is two-dimensional. Thus interactions between the two motors and MTBDs are ignored. This assumption is made to simplify the model. Other dynein models, like the winch model (\ref{sarlahmodel}), add in attractive and repulsive forces between the two motors which act in three dimensions. This model ignores such effects.\\

@@

Thus, if velocity equations can be found for the individual domains, then dynein's dynamic behavior can be solved for using numerical integration. The Brownian dynamics equation shown in Section (\ref{sec:bd}) provides velocity at time t from forces at time t. All that needs to be done is to come up with expressions for the forces on each domain, which is done in the next two sections.\\

@@

\subsection{Prestroke onebound model}
Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound. A spatial representation of onebound dynein is shown in Figure (\ref{fig:derivation-onebound}).

@@

As shown in Section (\ref{final-parameter-table}), the MT binding rate is much quicker than the unbinding rate. This means that, when just unbound, the rate of rebinding is very high. To prevent immediate rebinding, the model is given a ``rebinding immunity'' of a single timestep. During this immunity period, rebinding is not allowed.\\

@@

A series of conformational tests were done to test if the coordinate systems of either model worked. These are listed in Appendix (\ref{sec:conformational-tests}).\\

@@

To test if the models obey the ET, the total potential energy of each model was logged over $10^7$ timesteps of simulation. The results are reported in Figure (\ref{equipartition_agreement}), where the PE scale is in units of $\frac12 k_bT$. Energies are reported as a running average over the simulation from 0 to time $t$. As shown, both models have their average potential energy converge to the expected amount, where the onebound model has four degrees of freedom and the bothbound two.\\

@@

\section{Parameter fitting}
There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\theta_{m,eq}^{Pre}$, $\theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$. Each of these values influences the stepping behavior of the model, and so must be chosen wisely. Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table (\ref{parameter-table}). Others are more difficult to find. These values, including $k_b$, $k_ub$ and the three spring constants, must be found via fitting the model to experiment.\\

@@

\section{Model achieves processivity}
When the simulation is run at the parameters shown in (\ref{table:thesis-parameters}), the model exhibits stepping behavior, as shown in Figure (\ref{fig:stepping-trajectory}).\\

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$ & dt\\\hline
    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$ & $10^{-10}s$\\ \hline
  \end{tabular}
  \caption{Parameters used in processive simulations.}{These parameters cause processive stepping in the dynein model, as shown in Figures (\ref{fig:stepping-trajectory}) and (\ref{fig:final-histograms}).}
  \label{table:thesis-parameters}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
  \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation. The blue foot corresponds to the ``near'' dimer closer to the viewer, and the red to the far dimer. Top: x-projection of binding domains over time. The motor steps roughly 50nm in 10 $\mu s$. Middle: cartoon depictions of the model during simulation. In the cartoons the blue foot's position on the x-axis corresponds to the time axis on the top and bottom plots. That is, the first cartoon corresponds to dynein at roughly 1 $\mu s$. The first cartoon corresponds to a bothbound model, and the second cartoon corresponds to a onebound model. Bottom: y-projection of binding domains over time. Notice that only one binding domain is above 0nm at any time.}
  \label{fig:stepping-trajectory}
\end{figure}

Figures (\ref{fig:stepping-trajectory}) and (\ref{fig:stepping-trajectory}) demonstrate the model stepping five times, where a step constitutes lifting a binding domain off the microtubule for any amount of time. This behavior indicates that a springy hinge model with shifting equilibrium angles is capable of generating processive stepping behavior. Now that the model has demonstrated stepping behavior, it must be seen if it can generate steps at a size- and time-scale similar to that which real dynein takes in experiment.\\

Another important determination from Figure (\ref{fig:stepping-trajectory}) is the average position of the unbound foot is about 30\textit{nm} above the microtubule. This is a preliminary finding which may not represent how the model will behave once fit to stepping behavior, so drawing conclusive conclusions from it is impossible. However, it does initially suggest how dynein searches for the microtubule. Instead of hovering near the microtubule looking for a binding site, the motor pulls its foot away from the microtubule, diffusing until pushed downward far enough to bind. This behavior could explain why dynein's stepping pattern is so large: diffusing downward from 30\textit{nm} would allow significant x-diffusion along the microtubule. This could be contrasted with kinesin, which is smaller and could not move its foot so high off the microtubule.\\

@@

\section{Model step size is highly variant}
Figure (\ref{fig:final-histograms}) shows the stepping pattern of the model at the parameters shown in Table (\ref{table:thesis-parameters}). This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model. Note the model can generate 25nm steps, but has a high preference for <5nm steps. Also note that no backward steps are generated by the model. Simulation run at conditions in (\ref{table:thesis-parameters}). Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
    \label{fig:final-histograms}
\end{figure}

Figure (\ref{fig:final-histograms}) shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$. This is a very important result, since it indicates that the model is capable of taking a varied step size. This behavior is characteristic of dynein, and hence very important to reproduce.\\

The preference for $<5nm$ steps is very un-dynein-like. One explanation is that steps may be defined differently between experimental and modeled dynein. In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram. This may not be how the experiment in (\ref{fig:final-histograms}) records steps. Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely. A solution would thus be to lower the microtubule binding rate and see if the stepping histogram would level out. This may help, but may not, since lowering the binding rate would affect all binding probabilities, not just immediate rebindings.\\

@@

Comparing the simulation results in (\ref{fig:final-histograms}) with the experimental results in (\ref{fig:final-histograms}), it is clear that the model is still far from experimental dynein. However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein. It is very possible that changing the binding rate, unbinding rate and spring constants will change the stepping behavior of the model dramatically. Lowering the binding rate may even out the histogram and prevent instant rebinding. It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm. Another issue is the lack of backwards steps, which may also be solved by altering the spring constants.\\
